\Title

### 2021-06-25 manuscript/content.tex
Add a section on collocation (#160)
Included a paragraph on collocation explaining what it's use for and
that it suffers from the same computational limitations of EQL. Also
broke apart the paragraph where we compare all the different EQL papers.
It was huge and a bit difficult to follow. Had to add some text to the
location strategies part otherwise it would be a single sentence.

Measurements of anomalies in potential fields, like gravity disturbances and
total-field magnetic anomalies, are widely used in geophysical exploration for
their low cost of acquisition.
These data can be surveyed using ground, airborne, shipborne, or satellite
systems.
During ground surveys, the data are often gathered following irregular paths or
networks along the surface of the terrain, leading to highly variable
elevations in mountainous regions.
Airborne and satellite surveys gather data along flight lines, producing
closely spaced measurements along almost straight lines but with larger spacing
between adjacent lines.
Measurement height can also change because of the vertical movement of the
aircraft.
Processing of the data often involves interpolation onto a regular grid at
constant height, both to improve visualization for interpretation purposes as
well as to prepare the data for further processing and modelling (e.g.,
reduction-to-the-pole, derivative calculations, upward continuation, Euler
deconvolution).

Several methods exist in the literature for interpolation in two dimensions,
for example continuous curvature splines in tension \citep{smith1990},
bi-harmonic (thin-plate) splines \citep{sandwell1987}, and kriging
\citep{hansen1993}.
These general-purpose methods have limitations when it comes to interpolating
potential field data, namely
(i)~they are not able to take into account the variable height of the
observation points and
(ii)~the interpolating functions are not necessarily harmonic, which
is the underlying assumption behind many processing techniques
(e.g., upward continuation and vertical derivatives).

A widely used method for interpolating gravity and magnetic data
is the equivalent sources technique (also known as equivalent layer, radial
basis functions, or Green's functions interpolation).
First introduced by \citet{dampney1969}, the method consists in fitting a model
of finite elementary sources to the data and using this model to predict new
data values.
Besides interpolation, equivalent sources have been used for
reduction-to-the-pole of magnetic data
\citep{silva1986, nakatsuka2006, guspi2009}, upward
continuation \citep{emilia1973, li2010}, joint processing of gravity gradient
data \citep{barnes2011}, modelling the lithospheric magnetic field
\citep{kother2015}, recovering the magnetic induction vector from
total-field magnetic anomalies \citep{li2020}, and more.

@@

In the present study,
we propose two strategies for reducing the computational load of
the equivalent sources technique:

@@

The first strategy consists in dividing the survey area into horizontal blocks
and assigning a single source to each block, located at the median horizontal
location of the data points.
For airborne, shipborne, and satellite surveys, which are oversampled along
tracks, this can greatly reduce the size of the inverse problem while retaining
the same quality of interpolation.

The gradient boosting algorithm allows us to fit the equivalent source model
iteratively by operating on individual overlapping windows.
As a result, our method solves several much smaller least-squares problems
instead of a large one.
This has some similarities with the strategy used by \citet{leao1989} but
without the requirement for sources and predictions to be on regular grids.

Through tests on synthetic data, we show that:
(i)~the \emph{block-averaged} sources are able to achieve the same accuracy as
other traditional equivalent source layouts while using a fraction of the
number of sources, and
(ii)~the \emph{gradient boosting} algorithm greatly reduces the computational
memory required to fit very large datasets without sacrificing prediction
accuracy.
Finally, a combination of both strategies is used to process a collection of
approximately 1.7 million ground gravity data measurements from Australia.

>>>>

Measurements of anomalies in potential fields, like gravity disturbances and
total-field magnetic anomalies, are widely used in geophysical exploration for
their relatively low cost of acquisition.
These data can be surveyed using ground, airborne, shipborne, or satellite
systems.
In ground surveys, the data are often gathered following irregular paths or
networks along the surface of the terrain, leading to highly variable
elevations in mountainous regions.
On airborne surveys, the data are gathered along flight lines, producing a
large number of measurements concentrated along almost straight lines.
Measurement height can also change because of the vertical movement of the
aircraft.
Processing of the data often involves interpolation onto a regular grid at
constant height, both to improve visualization for interpretation purposes as
well as to prepare the data for further processing and modelling (e.g.,
reduction-to-the-pole, derivative calculations, upward continuation, Euler
deconvolution).

Several methods exist in the literature for interpolation in two dimensions,
for example continuous curvature splines in tension \citep{smith1990},
bi-harmonic (thin-plate) splines \citep{sandwell1987}, and kriging \citep{hansen1993}.
These general-purpose methods have limitations when it comes to interpolating
potential field data:
(i)~they are not able to take into account the variable height of the
observation points and
(ii)~the interpolating functions are not necessarily harmonic, which
is the underlying assumption behind many processing techniques
(e.g., upward continuation and vertical derivatives).

A widely used method for interpolating gravity and magnetic data
is the equivalent sources technique (also known as equivalent layer, radial
basis functions, or Green's functions interpolation), first introduced by
\citet{dampney1969}.
It consists in fitting a model of finite elementary sources to the data and
using this model to predict new data values.
Besides interpolation, equivalent sources have been used for
reduction-to-the-pole of magnetic data
\citep{silva1986, nakatsuka2006, guspi2009}, upward
continuation \citep{emilia1973, li2010}, joint processing of gravity gradient
data \citep{barnes2011}, modelling the lithospheric magnetic field
\citep{kother2015}, recovering the magnetic induction vector from
total-field magnetic anomalies \citep{li2020}, and more.

@@

In the present study,
we propose a two strategies for reducing the computational load of
the equivalent sources technique:

@@

The first strategy consists in dividing the survey area into horizontal blocks
and assign one source to each block, located at the median horizontal location
of the data points. For airborne, shipborne, and satellite surveys, which are
oversampled along tracks, this can greatly reduce the size of the inverse
problem while retaining the same quality of interpolation.

The gradient boosting algorithm allows us to fit the equivalent source model
iteratively by operating on individual overlapping windows.
Thus, our method solves several much smaller least-squares problems instead of
a large one.
This has some similarities with the strategy used by \citet{leao1989} but
without the requirement for sources and predictions to be on regular grids.

Through tests on synthetic data, we show that:
(i)~the \emph{block-averaged} sources are able to achieve the same accuracy as
other traditional equivalent source layouts while using a fraction of the
number of sources, and
(ii)~the \emph{gradient boosting} algorithm greatly reduces the computational
memory required to fit very large datasets without sacrificing prediction
accuracy.
Finally, a combination of both strategies is used to process a collection of
around 1.7 million ground gravity data measurements from Australia.
